Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-07 bbbq_article.tex
Main text points to tables in supmat

Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.

@@

\input{bbbq_1/table_f_tmh.latex}

@@

\input{bbbq_1/table_tmh_binders_mhc1.latex}

%\begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1/bbbq_1_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium tuberculosis for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_myco}
% \end{table}

@@

\input{bbbq_1/table_tmh_binders_mhc2.latex}

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_2/bbbq_2_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and 
      Mycobacterium tuberculosis for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_myco}
% \end{table}

>>>>

Figure \ref{fig:2} shows the percentages of MHC-II epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (tables \ref{tab:tmh_binders_mhc1} 
and \ref{tab:tmh_binders_mhc2}) for the TMH and epitope counts.

@@

% Percentage of spots and spots that overlap with a TMH
\input{bbbq_1_fast/table_f_tmh.latex}

@@

% Percentage of MHC-I 9-mers overlapping with TMH. Values in brackets
% show the number of binders that have at least one residue overlapping with a
% TMH (first value)as well as the number of binders (second value). Percentile
% used: 0.02
% Label: tab:tmh_binders_mhc1
\input{bbbq_1_fast/table_tmh_binders_mhc1.latex}

%\begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_1_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_1_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium tuberculosis for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_myco}
% \end{table}

@@

\input{bbbq_1_fast/table_tmh_binders_mhc2.latex}

% \begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_2_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_2_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and 
      Mycobacterium tuberculosis for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_myco}
% \end{table}
